---
title: "Introduction to rgtracker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rgtracker-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

devtools::load_all(".")
```

```{r setup}
library(rgtracker)
```

While teaching at UBC is a challenging and demanding job, teaching in the Master of Data Science (MDS) program is even tougher as this is an accelerated program. Needless to say, the MDS teaching team is under a lot of stress when it comes to managing students' grade and adjusting the courses difficulties.

As a result, our team has come up with a good solution for instructors to reduce their workload on handling the grades. With our handy package, instructors can:

- Register MDS courses
- Record weekly grades
- Calculate course statistics such as mean, median, 1st or 3rd quantile
- Rank courses
- Rank students
- Calculate final grades for each course
- Adjust the students' grades

## Data: An imaginary cohort

```{r, include = FALSE}
courses <- data.frame(
  course_id = c(511, 522),
  lab1 = c(0.15, 0),
  lab2 = c(0.15, 0),
  lab3 = c(0.15, 0),
  lab4 = c(0.15, 0),
  quiz1 = c(0.2, 0),
  quiz2 = c(0.2, 0),
  milestone1 = c(0, 0.1),
  milestone2 = c(0, 0.2),
  milestone3 = c(0, 0.2),
  milestone4 = c(0, 0.3),
  feedback = c(0, 0.2)
)

grades <- data.frame(
  course_id = c(511, 511, 511, 511, 522, 522, 522, 522),
  student_id = c("tom", "tiff", "mike", "joel", "tom", "tiff", "mike", "joel"),
  lab1 = c(100, 87.6, 84.4, 100, 0, 0, 0, 0),
  lab2 = c(100, 100, 79.6, 100, 0, 0, 0, 0),
  lab3 = c(79.2, 81.2, 75.2, 99.6, 0, 0, 0, 0),
  lab4 = c(83.6, 89.2, 98.8, 71.2, 0, 0, 0, 0),
  quiz1 = c(75.6, 100, 84.8, 96.8, 0, 0, 0, 0),
  quiz2 = c(75.6, 73.2, 100, 79.2, 0, 0, 0, 0),
  milestone1 = c(0, 0, 0, 0, 100, 100, 92, 98.4),
  milestone2 = c(0, 0, 0, 0, 97.6, 77.2, 75.6, 85.6),
  milestone3 = c(0, 0, 0, 0, 80, 76.8, 97.6, 96.8),
  milestone4 = c(0, 0, 0, 0, 100, 100, 84.4, 100),
  feedback = c(0, 0, 0, 0, 100, 85.6, 98.8, 82.4)
)
```

```{r Data Summary}
courses

grades
```

