---
title: "Introduction to rgtracker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rgtracker-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

devtools::load_all(".")
```

```{r setup}
library(rgtracker)
```

While teaching at UBC is a challenging and demanding job, teaching in the Master of Data Science (MDS) program is even tougher as this is an accelerated program. Needless to say, the MDS teaching team is under a lot of stress when it comes to managing students' grade and adjusting the courses difficulties.

As a result, our team has come up with a good solution for instructors to reduce their workload on handling the grades. With our handy package, instructors can:

- Register MDS courses
- Record weekly grades
- Calculate course statistics such as mean, median, 1st or 3rd quantile
- Rank courses
- Rank students
- Calculate final grades for each course
- Adjust the students' grades

```{r, include = FALSE}
course_details <- readr::read_csv('course_info.csv')
grade_details <- readr::read_csv('grade_info.csv')
```

## Register courses

It is the beginning of a new school year, and our beloved instructors need to register for new courses in the system.

```{r Show raw courses data}
course_details %>%
  head(3)
```
They can simply call the `register_courses` function in order to transform the data into a tidy data frame. In addition, it will also perform additional checks to make sure the `course_id` and `assessment_id` are in a list of predefined values, and the latter will be between 0 and 1 with all components for 1 course add up to 1.

```{r Register courses}
courses <- register_courses(course_details)
  
courses
```

## Record grades

Continuous assessment is an effective way to assess how well the students understand the materials. For the majority of classes, these components consist of weekly labs and fortnightly quizzes. However, for some particular courses, there are unique components such as "Peer Review", "Milestone"... Instructors can effortlessly record these grades by calling the `record_grades` function. In addition, additional data sanity checks are also conducted to make sure the `course_id` and `assessment_id` are in a list of predefined values, and the grades must be between 0 and 100.

```{r Record grades}
grades <- record_grades(grade_details)
  
grades
```
